---
title: "agreement_round1"
author: "Alina Koppold"
date: "2023-05-10"
output: html_document
---

```{r setup, include=FALSE}
rm(list = ls())
knitr::opts_chunk$set(echo = F,
                      message = F)
library(readr)
library(tidyverse)
library(crosstable)
library(irr)
```


```{r data-impport}
odd <- read_csv("data/Round 1 Screening - Sheet1 (screener_id ODD).csv") %>% drop_na(unique_id) %>% select(1,7, 8,9)
even <- read_csv("data/Round 1 Screening - Sheet2 (screener_id EVEN).csv")%>% drop_na(unique_id) %>% select(1,7, 8,9)
```

```{r data-wrangle}
df.all = merge(odd, even, by = "unique_id")
names(df.all) = c("unique_id", "require_full_text_odd", "screening_odd", "screener_odd", 
                  "require_full_text_even", "screening_even", "screener_even")

# check and remove typos
test = df.all %>% filter(require_full_text_odd =="o")
df.all$require_full_text_odd[df.all$require_full_text_odd == "o"] <- 0
```

## Agreement on screening between even and odd
### crosstable 1 shows typos in sheet

```{r c1}
crosstable(df.all, screening_odd, by=screening_even, total="both") %>%
  as_flextable(keep_id=FALSE)
```

### crosstable 2 correct one
```{r c1-corr}
# fixing typos 
# for odd
df.all$screening_odd[df.all$screening_odd == "exlcude"] <- "exclude"
df.all$screening_odd[df.all$screening_odd == "incldue"] <- "include"
df.all$screening_odd[df.all$screening_odd == "unsure"] <- "uncertain"
# for even
df.all$screening_even[df.all$screening_even == "exlcude"] <- "exclude"


# check again
crosstable(df.all, screening_odd, by=screening_even, total="both") %>%
  as_flextable(keep_id=FALSE)
```


## Moderate agreement (Cohen's Kappa) between rater *odd* and rater *even* with respect to the screening decision (exclude, include, uncertain) was observed for round one: 
```{r kappa}
kappa2(df.all[,c(3,6)], "unweighted")
```


## Even/ odd crosstable comparison about full text required
```{r c2}
crosstable(df.all, require_full_text_odd, by=require_full_text_even, total="both") %>%
  as_flextable(keep_id=FALSE)
```


## alternative: S-index 
```{r s-index}
source("https://raw.githubusercontent.com/rnorouzian/m/master/r.r")
irr(df.all[,c(3,6)])
```

# testing the lack of kappa 
```{r}

v1 = c("ELF","ELF","ELF","ELF","ELF","ELF","ELF","ELF","ELS","ELS", "ELF","ELF","ELF","ELF","ELF","ELF","ELF","ELF","ELS","ELS")
v2 = c("ELF","ELF","ELF","ELF","ELF","ELF","ELF","ELF","ELF","ELF", "ELF","ELF","ELF","ELF","ELF","ELF","ELF","ELF","ELF","ELF")
test = as.data.frame(cbind(v1,v2))
test$v1 = as.factor(test$v1)
test$v2 = as.factor(test$v2)
irr::kappa2(test, "unweighted")
irr(test)
```


*end